---
title       : Coursera "Developing Data Products" Assignment
subtitle    : Shiny App Description
author      : Ioanna Aristeidopoulou
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
---

## Description of my Shiny Application

The purpose of this application is to allow the user explore the US State data.

- The user selects the data dimension he/she wants to display.
  This can be one of the following:
  - Population, 
  - Income, 
  - Illiteracy, 
  - Life.Exp, 
  - Murder, 
  - HS.Grad, 
  - Frost, 
  - Area.      
- An intensity map is displayed for the selected dimension  
- The color intensity of each state corresponds to the value of the selected dimension

--- .class #id 

## ui.R Code

This is the user interface part of my shiny app:

```{r eval=FALSE}
library(shiny)
require(datasets)
states <- data.frame(state.name, state.x77)
shinyUI(fluidPage(
        # Application title
        titlePanel("US State Data"),
        # Sidebar with controls to select the data index to display in Geo Chart
        sidebarLayout(sidebarPanel(
                selectInput("dataIndex", "Select Data Index:", choices=colnames(states[,-1])),hr()),
                # Show the google map
                mainPanel(h3(textOutput("dataIndex")),htmlOutput("view")))))
```

--- .class #id 
## server.R Code

This is the server part of my shiny app:

```{r eval=FALSE}
library(shiny)
library(googleVis)
require(datasets)
states <- data.frame(state.name, state.x77)
shinyServer(function(input, output) {
        output$dataIndex <- reactive({
         switch(input$dataIndex,"Population" = "Population",
                "Income" = "Income", "Illiteracy" = "Illiteracy",
                "Life.Exp" = "Life.Exp", "Murder" = "Murder",
                "HS.Grad" = "HS.Grad","Frost" = "Frost","Area" = "Area")})
 output$view <- renderGvis({
 gvisGeoChart(states, locationvar = "state.name", colorvar = input$dataIndex,options=list(region="US", 
displayMode="regions", resolution="provinces",width=600, height=400))})
})
```

--- .class #id 
## US State Intensity Map

<div align="center">
<iframe 
src="http://iaristeid.shinyapps.io/DataProducts/" >
  </iframe></div>


```{r, echo=FALSE, chart1, fig.show='asis', results='asis', fig.align='center'}
suppressPackageStartupMessages(library(googleVis))
require(datasets)
states <- data.frame(state.name, state.x77)
geo1 <- gvisGeoChart(states, locationvar = "state.name", colorvar = "Population",options=list(region="US", displayMode="regions", resolution="provinces",width = 200, height = 100))
print(geo1, "chart")
```

